---
title: "DWF Rate for ECE & ME Departments"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(dplyr)
library(flexdashboard)
library(readr)
CSE_ALL_ENR_up2020 <- read_csv("V1CSE_ALL_ENR_up2020.csv", 
    col_types = cols(X1 = col_skip()))

CSE_ALL_ENR_up2020_ENG_1920 <- CSE_ALL_ENR_up2020 %>% filter(COHORT_YEAR>=20192020 &( ENTRY_DEPARTMENT=="Mechanical Engineering"|ENTRY_DEPARTMENT=="Electrical and Computer Engineering")) %>% select(1,2,contains("PROGRAM"),contains("DEPARTMENT"),contains("GPA"),"APPLICANT_TIER")

CRS_ALL_up2020 <- read_csv("CRS_ALL_up2020.csv", 
    col_types = cols(X1 = col_skip()))

CRS_ALL_up1920 <- CRS_ALL_up2020 %>%  filter(COHORT_YEAR>=20192020)

ALLCRSGRADE <- merge(CSE_ALL_ENR_up2020_ENG_1920,CRS_ALL_up1920, by="UNIV_ROW_ID", all.x=T)
```

First mean GPA of ECE and ME Departments for FTIC
======================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### 1st GPA Trends for ECE & ME

```{r}

CSE_ALL_ENR_up2020[which(is.na(CSE_ALL_ENR_up2020$FIRST_FALL_GPA)),"FIRST_FALL_GPA"] <- 0
CSE_ALL_ENR_up20201 <- CSE_ALL_ENR_up2020 %>% filter(ENTRY_DEPARTMENT=="Mechanical Engineering"|ENTRY_DEPARTMENT=="Electrical and Computer Engineering") %>% group_by(ENTRY_DEPARTMENT,COHORT_YEAR) %>% summarise(Mean1stGPA=round(mean(FIRST_FALL_GPA, na.rm=T),3), .groups="drop", Counts=n())

library(DT)
datatable(CSE_ALL_ENR_up20201, extensions = "Buttons",caption = "1st GPA for Engineering",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
```

DWF / Pass Rates by 1st Fall Course Name
====================================================================


Column {data-width=650}
-----------------------------------------------------------------------

### Pass Rates Comparison (2019 vs. 2020)

```{r}
library(dplyr)
library(DT)
ALLCRSGRADE1920 <- ALLCRSGRADE %>% filter((COHORT_YEAR.x==20192020 & DEMO_TIME_FRAME==201908) |( COHORT_YEAR.x==20202021 & DEMO_TIME_FRAME==202008)) 
ALLCRSGRADE1920$DWF <- ALLCRSGRADE1920$GRADE_AWARDED
ALLCRSGRADE1920$DWF1 <- sapply(ALLCRSGRADE1920[,16], function(x) replace(x, x %in% c("D","D+","W","F","NF","I","I*","U"), "failed"))
ALLCRSGRADE1920 <- ALLCRSGRADE1920 %>% mutate(DWF2 = ifelse(DWF1=="failed","DWF","Pass"))
### 2019
ALLCRSGRADE19 <- ALLCRSGRADE1920 %>% filter(COHORT_YEAR.x==20192020)
tabENG19 <- table(ALLCRSGRADE19$COURSE_NAME,ALLCRSGRADE19$DWF2)
tabmarg <- addmargins(tabENG19)
tab19ENG <- as.data.frame.matrix(tabmarg)
tab19ENG$COURSE_NAME <- rownames(tabmarg)
tab19ENG <- tab19ENG %>% select(4,1:3)
colnames(tab19ENG) <- c("COURSE_NAME","CountsDWF2019","CountsPass2019","TotalSum2019")
###2020
ALLCRSGRADE20 <- ALLCRSGRADE1920 %>% filter(COHORT_YEAR.x==20202021)
tabENG20 <- table(ALLCRSGRADE20$COURSE_NAME,ALLCRSGRADE20$DWF2)
tabmarg20 <- addmargins(tabENG20)
tab20ENG <- as.data.frame.matrix(tabmarg20)
tab20ENG$COURSE_NAME <- rownames(tabmarg20)
tab20ENG <- tab20ENG %>% select(4,1:3)
colnames(tab20ENG) <- c("COURSE_NAME","CountsDWF2020","CountsPass2020","TotalSum2020")
tab20ENG1 <- tab20ENG[-1,]

ENGCRS1920 <- merge(tab19ENG,tab20ENG, by=c("COURSE_NAME"), all=T) %>% mutate(PassRate2019=round(CountsPass2019/TotalSum2019,2), PassRate2020=round(CountsPass2020/TotalSum2020,2))

library(DT)
datatable(ENGCRS1920[-1,], extensions = "Buttons",caption = "PASS Rate by Courses for ECE & ME (FT19 vs. FT20)",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
```

DWF Counts by Course Sections
=====================================================================

Column {.tabset .tabset-fade data-width=650}
-----------------------------------------------------------------------

### DWF by sections

```{r}

ALLCRSGRADE20 <- ALLCRSGRADE1920 %>% filter(COHORT_YEAR.x==20202021)
tabENG20SEC <- table(ALLCRSGRADE20$CRS_SECTN_NBR,ALLCRSGRADE20$DWF2)
tabmarg20SEC <- addmargins(tabENG20SEC)
tab20ENGSEC <- as.data.frame.matrix(tabmarg20SEC)
tab20ENGSEC$COURSE_NAME <- rownames(tabmarg20SEC)
tab20ENGSEC <- tab20ENGSEC %>% select(4,1:3)
colnames(tab20ENGSEC) <- c("CRS_SECTN_NBR","CountsDWF2020","CountsPass2020","TotalSum2020")
ALLCRSGRADE20cols <- ALLCRSGRADE20 %>% select("COURSE_NAME","CRS_SECTN_NBR")
ALLCRSGRADE20cols1 <- ALLCRSGRADE20cols[!duplicated(ALLCRSGRADE20cols[c(1,2)]),]



tab20ENGSEC1 <- merge(ALLCRSGRADE20cols1,tab20ENGSEC, by="CRS_SECTN_NBR",all = T)
tab20ENGSEC1 <- tab20ENGSEC1 %>% select(2,1,3:5)

library(DT)
datatable(tab20ENGSEC1[tab20ENG1$COURSE_NAME != 410228,], extensions = "Buttons",caption = "Counts Pass/DWF by Sections",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
```

### Is there any difference between AM and PM Sections of EEL 4834?

```{r}
## converted letter grades to numeric
library(rpivotTable)
ALLCRSGRADE20$GradePoints <- sapply(ALLCRSGRADE20[,16], function(x) replace(x, x %in% c("W","F","I*","S","NF","XX","I","U","P","NG"), 0))
# passing grades
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="A", "GradePoints"] <- "4.0"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="A-", "GradePoints"] <- "3.70"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="B", "GradePoints"] <- "3.0"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="B+", "GradePoints"] <- "3.30"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="B-", "GradePoints"] <- "2.70"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="C-", "GradePoints"] <- "1.70"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="C+", "GradePoints"] <- "2.30"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="C", "GradePoints"] <- "2.00"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="D", "GradePoints"] <- "1.0"
ALLCRSGRADE20[ALLCRSGRADE20$GradePoints=="D+", "GradePoints"] <- "1.30"
ALLCRSGRADE20$GradePoints <- as.numeric(ALLCRSGRADE20$GradePoints)

# DWf col
ALLCRSGRADE20$DWF1 <- sapply(ALLCRSGRADE20[,16], function(x) replace(x, x %in% c("W","F","I*","NF","I","U","NG","D","D+"), "failed"))
ALLCRSGRADE20 <- ALLCRSGRADE20 %>% mutate(DWF2 = ifelse(DWF1=="failed","DWF","Pass"))

#filter for EEL4834
CRS_ALL_up2020_EEL4834 <- ALLCRSGRADE20 %>% filter(COHORT_YEAR.x>=20202021 & COURSE_NAME== "EEL4834") %>% group_by(CRS_SECTN_NBR) %>% mutate(CRS_TIME=ifelse(CRS_SECTN_NBR<=80575,"AM","PM")) %>% select(COURSE_NAME,CRS_SECTN_NBR,CRS_TIME,DWF,DWF2,GradePoints)
#CRS_ALL_up2020_EEL4834$CRS_SECTN_NBR <- as.factor(CRS_ALL_up2020_EEL4834$CRS_SECTN_NBR)

#anyNA(CRS_ALL_up2020_EEL4834$GradePoints)


AM <- CRS_ALL_up2020_EEL4834 %>% filter(CRS_TIME=="AM") %>% select(COURSE_NAME,CRS_SECTN_NBR,GradePoints)
PM <- CRS_ALL_up2020_EEL4834  %>% filter(CRS_TIME=="PM") %>% select(COURSE_NAME,CRS_SECTN_NBR,GradePoints)

myt <- t.test(AM$GradePoints, PM$GradePoints)
mytSTAT <- CRS_ALL_up2020_EEL4834 %>% group_by(CRS_TIME) %>% summarise(MeanGP=mean(GradePoints), SD=sd(GradePoints), Counts=n(), .groups='drop')
mytSTAT

rpivotTable(CRS_ALL_up2020_EEL4834, aggregatorName = "Count as Fraction of Rows",
            rows = c("COURSE_NAME","CRS_TIME"),
            
            cols = c("DWF2"),
           
            subtotals = T, rendererName = "Table With Subtotal")
```
* The letter grades are converted to grade points (i.e. A = 4.00)
* AM and PM sections each contain 18 and 11 FTICs.
* The means of AM (x) and PM sections' performance are 2.905 and 2.39.



###  CHM2045/L

```{r}
#filter for CHM2045
CRSCHM2045 <- ALLCRSGRADE20 %>% filter(COHORT_YEAR.x>=20202021 & COURSE_NAME== "CHM2045" & DEMO_TIME_FRAME == 202008) %>% arrange(CRS_SECTN_NBR) %>% select(COURSE_NAME,CRS_SECTN_NBR,DWF,DWF2,GradePoints) %>% filter(CRS_SECTN_NBR==81816 | CRS_SECTN_NBR== 81817 | CRS_SECTN_NBR== 81818 |CRS_SECTN_NBR == 81820 |CRS_SECTN_NBR== 81821 | CRS_SECTN_NBR== 81822 )%>% mutate(CRS_TIME= ifelse(CRS_SECTN_NBR<= 81818,"AM","PM"), Inst=ifelse(CRS_TIME=="MWF_AM","Dr.Whitaker","Dr.Filds-Wolf")) %>% select(-7)

#CHM2045L
CRSCHM2045L <- ALLCRSGRADE20 %>% filter(COHORT_YEAR.x>=20202021 & COURSE_NAME== "CHM2045L" & DEMO_TIME_FRAME == 202008) %>% arrange(CRS_SECTN_NBR) %>% select(COURSE_NAME,CRS_SECTN_NBR,DWF,DWF2,GradePoints) %>% 
  filter(CRS_SECTN_NBR==80072 | CRS_SECTN_NBR== 81006 | CRS_SECTN_NBR == 80071 |CRS_SECTN_NBR== 82719)%>% 
  mutate(CRS_TIME= ifelse(CRS_SECTN_NBR== 80072,"W_12:30P",ifelse(CRS_SECTN_NBR== 81006,"W_5:30P", ifelse(CRS_SECTN_NBR== 80071,"T_5:00P", ifelse(CRS_SECTN_NBR== 82719,"T_8:00A","else"))))) %>% mutate(Inst=ifelse(CRS_TIME=="W_12:30P","Dr.Cornwall",ifelse(CRS_TIME=="W_5:30P","Dr.Li", ifelse(CRS_TIME=="T_5:00P","Dr.Barnes", ifelse(CRS_TIME=="T_8:00A","Dr.Mena","else"))))) %>% select(-7)


CRSCHM2045L$CRS_SECTN_NBR <- as.factor(CRSCHM2045L$CRS_SECTN_NBR)
#CRSCHM2045$CRS_SECTN_NBR <- as.factor(CRSCHM2045$CRS_SECTN_NBR)

#anyNA(CRS_ALL_up2020_EEL4834$GradePoints)


AM <- CRSCHM2045 %>% filter(CRS_TIME=="AM") %>% select(CRS_SECTN_NBR,GradePoints)
pM <- CRSCHM2045 %>% filter(CRS_TIME=="PM") %>% select(CRS_SECTN_NBR,GradePoints)
myCHMall <- rbind(CRSCHM2045,CRSCHM2045L)

myCHM <- t.test(AM$GradePoints, PM$GradePoints)
myCHMSTAT<- myCHMall %>% group_by(COURSE_NAME,CRS_TIME) %>% summarise(MeanGP=mean(GradePoints), SD=sd(GradePoints), Counts=n(), .groups='drop')
myCHMSTAT

library(rpivotTable)

myCHMall <- rbind(CRSCHM2045,CRSCHM2045L)

rpivotTable(myCHMall, aggregatorName = "Count as Fraction of Rows",
            rows = c("COURSE_NAME","CRS_TIME"),
            
            cols = c("DWF2"),
           
            subtotals = T, rendererName = "Table With Subtotal")
```

###  MAC1147

```{r}
#filter for CHM2045
CRSMAC1147<- ALLCRSGRADE20 %>% filter(COHORT_YEAR.x>=20202021 & COURSE_NAME== "MAC1147" & DEMO_TIME_FRAME == 202008) %>% arrange(CRS_SECTN_NBR) %>% select(COURSE_NAME,CRS_SECTN_NBR,DWF,DWF2,GradePoints) 

df <- CRSMAC1147 %>% select(COURSE_NAME,CRS_SECTN_NBR)
namenumber1 <- df[!duplicated(df$CRS_SECTN_NBR),]
namenumber1$CRS_Day <- c("Fri","Fri","Fri","Fri","Fri","Fri","Fri","Fri","Fri","Fri","Fri","Thu","Fri","Fri","Thu")
namenumber1$CRS_TIME <- c("AM","AM","PM","PM","AM","AM","PM","PM","AM","AM","PM","PM","AM","PM","AM")

CRSMAC1147_a <- merge(namenumber1,CRSMAC1147, by=c("COURSE_NAME","CRS_SECTN_NBR"), all.x=T) %>% select(1,2,4,5,6,7)
#CRSMAC1147_a$Inst <- rep("Dr.Kim")
AM <- CRSMAC1147_a %>% filter(CRS_TIME=="AM") %>% select(CRS_SECTN_NBR,GradePoints)
pM <- CRSMAC1147_a %>% filter(CRS_TIME=="PM") %>% select(CRS_SECTN_NBR,GradePoints)

myMAC1147<- t.test(AM$GradePoints, PM$GradePoints)
myMAC1147STAT <- CRSMAC1147_a %>% group_by(CRS_TIME) %>% summarise(MeanGP=mean(GradePoints), SD=sd(GradePoints), Counts=n(), .groups='drop')
myMAC1147STAT
library(DT)
library(rpivotTable)
rpivotTable(CRSMAC1147_a, aggregatorName = "Count as Fraction of Rows",
            rows = c("COURSE_NAME","CRS_TIME"),
            
            cols = c("DWF2"),
           
            subtotals = T, rendererName = "Table With Subtotal")
```

###  MAC 2311

```{r}
#filter for MAC 2311
CRSMAC2311<- ALLCRSGRADE20 %>% filter(COHORT_YEAR.x>=20202021 & COURSE_NAME== "MAC2311" & DEMO_TIME_FRAME == 202008) %>% arrange(CRS_SECTN_NBR) %>% select(COURSE_NAME,CRS_SECTN_NBR,DWF,DWF2,GradePoints)

df1 <- CRSMAC2311 %>% select(COURSE_NAME,CRS_SECTN_NBR)
namenumber11 <- df1[!duplicated(df1$CRS_SECTN_NBR),]
namenumber11$CRS_Day <- c("MWF","TTF","MWF","TTF","TTF","MWF","MWF","TTF")
namenumber11$CRS_TIME <- c("AM","PM","AM","AM","PM","PM","PM","AM")

CRSMAC2311_a <- merge(namenumber11,CRSMAC2311, by=c("COURSE_NAME","CRS_SECTN_NBR"), all.x=T) %>% select(1,2,4,5,6,7)
#CRSMAC2311_a$Inst <- rep("Dr.Nguyen")
AM <- CRSMAC2311_a %>% filter(CRS_TIME=="AM") %>% select(CRS_SECTN_NBR,GradePoints)
pM <- CRSMAC2311_a %>% filter(CRS_TIME=="PM") %>% select(CRS_SECTN_NBR,GradePoints)

myMAC2311 <-  t.test(AM$GradePoints, PM$GradePoints)
myMAC2311STAT<- CRSMAC2311_a %>% group_by(CRS_TIME) %>% summarise(MeanGP=mean(GradePoints), SD=sd(GradePoints), Counts=n(), .groups='drop')
myMAC2311STAT

rpivotTable(CRSMAC2311_a, aggregatorName = "Count as Fraction of Rows",
            rows = c("COURSE_NAME","CRS_TIME"),
            
            cols = c("DWF2"),
           
            subtotals = T, rendererName = "Table With Subtotal")
```

### Data Table

```{r}
library(dplyr)
library(DT)
allAMPM <- rbind(CRS_ALL_up2020_EEL4834,CRSCHM2045)
allAMPM1 <- rbind(allAMPM,CRSMAC1147_a)
allAMPM2 <- rbind(allAMPM1,CRSMAC2311_a)
allAMPM2$COURSE_NAME <- as.factor(allAMPM2$COURSE_NAME)
av1 <- aov(GradePoints ~ COURSE_NAME+CRS_TIME, data = allAMPM2)
datatable(allAMPM2, extensions = "Buttons",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
```


Summary
========================================================================


### About Summary

This information is for ECE (Electrical and Computer Engineering) and ME (Mechanical Engineering).


* The 1st GPA for ECE FTIC 2020 decreased from 2.919 to 2.848.
* The 1st GPA for ME FTIC 2020 increased from 2.729 to 2.952.
* The passing rates for ECE and ME FTIC in 2020 changed as follows:
* CHM 2045 - from 0.87 to 0.85.
* MAC 1147 - from 0.84 to 0.74.
* MAC 1105C - from 0.73 to 0.60.
* MAc 2311 - from 0.79 to 0.82.
* EEL 4834 - from  0.80 to 0.72.
* EGS 1006 - from 0.91 to 0.82.
* More courses and passing rates are available on the tab named 'DWF/Pass Rates by 1st Fall Course Name'.



